---
title: "InteractivePlot"
author: "Laura Garner"
date: "11 May 2019"
output: ioslides_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
library(plotly)
library(dplyr)
```

## Data

The data for this presentation has been sourced from the Open Data portal of the Queensland Government, Australia www.data.qld.gov.au 

The specific dataset relates to factors involved in crashes on Queensland roads between 2001 and 2018, and the plot created focuses on crashes where a contributing factor was drink driving.

```{r data}

data<- read.csv("http://www.tmr.qld.gov.au/~/media/aboutus/corpinfo/Open%20data/crash/factorsinroadcrashes.csv")

data<- data[data$Involving_Drink_Driving == "Yes",]
dd<- data %>%
        select(Crash_Year, Crash_Severity, Count_Crashes, Count_All_Casualties) %>%
        group_by(Crash_Year, Crash_Severity) %>%
        summarise(Crash = sum(Count_Crashes), Casualties = sum(Count_All_Casualties))
```

## Plot

Plot showing the number of casualties involved in road crashes where drink driving was a causing factor.

```{r plot}

plot_ly(dd, x = dd$Crash_Year, y = dd$Casualties, z = dd$Crash, color = dd$Crash_Severity, mode = "marker", type = 'scatter3d')
```

